---
title: "MyTien's Analysis"
author: "MyTien Kien; kmytien"
date: "4/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)

main <- readr::read_csv('./excel_files/data.csv')
by_artist <- readr::read_csv('./excel_files/data_by_artist.csv')
by_genre <- readr::read_csv('./excel_files/data_by_genres.csv')
by_year <- readr::read_csv('./excel_files/data_by_year.csv')

main <- drop_na(main)
```

## Final Project Questions

**1.** Does a success of a song depend on the date of the song released?
```{r}

```


**2.** Does the popularity of a song depend on the danceability and loudness?
```{r}

```


**3.** What is the relationship between energy and loudness in a song?
```{r}
#Going to go more into depth, just starting for now
q3 <- main %>% ggplot(aes(x = loudness, y = energy)) + geom_point() +
      ggtitle("Loudness v.s. Energy")
q3
```


**4.** How does the popularity of the artist affect how successful the song will be?
```{r}
#Going to measure success of a song by danceability - can change later if needed

#Low Danceability
dance_low <- main %>% filter(danceability <= 0.5) %>%
      select(artists, popularity, name, danceability)

#High Danceability
dance_high <- main %>% filter(danceability > 0.5) %>%
      select(artists, popularity, name, danceability)
```

```{r}
#Plot for Low Danceability - ggplot?

#Plot for High Danceability

```


**5.** Analyze relationship between temp and acousticness.
```{r}

```


**6.** What is the greatest predictor of a song's popularity?
```{r}

```


**7.**
```{r}

```


**8.**
```{r}

```

