---
title: "MyTien's Analysis"
author: "MyTien Kien; kmytien"
date: "4/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)

main <- readr::read_csv('./excel_files/data.csv')
by_artist <- readr::read_csv('./excel_files/data_by_artist.csv')
by_genre <- readr::read_csv('./excel_files/data_by_genres.csv')
by_year <- readr::read_csv('./excel_files/data_by_year.csv')

main <- drop_na(main)
```

## Final Project Questions

**1.** Does a success of a song depend on the date of the song released?
```{r}

```


**2.** Does the popularity of a song depend on the danceability and loudness?
```{r}

```


**3.** What were the five most popular songs in 2020? Is there a correlation with popularity and energy?
```{r}
#not finished
q3 <- main %>%
      filter(year == 2020) %>%
      select(artists, name, popularity, energy) %>%
      arrange(desc(popularity)) %>%
      head(5)

```


**4.** Analyze how song trends (danceability, energy, etc..), changed throughout each year.
```{r}
q4 <- main %>% 
      group_by(year) %>%
      summarise(danceability = mean(danceability),
                acousticness = mean(acousticness),
                energy = mean(energy),
                valence = mean(valence),
                liveness = mean(liveness))

q4
```

```{r}
#Plot for song trends
q4 <- q4 %>% pivot_longer(danceability:liveness, names_to = 'trend', values_to = 'value')

q4_plot <- q4 %>% 
      ggplot(aes(x = year, y = value, color = trend)) + geom_line() + 
      ggtitle("Trends Throughout the Years")

q4_plot
```


**5.** Analyze relationship between temp and acousticness.
```{r}

```


**6.** What is the greatest predictor of a song's popularity?
```{r}

```


**7.**
```{r}

```


**8.**
```{r}

```

