---
title: "Sakeths_analysis"
author: "Saketh Jonnadula"
date: "4/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r warning=FALSE, message=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)

main <- readr::read_csv('./excel_files/data.csv')
by_artist <- readr::read_csv('./excel_files/data_by_artist.csv')
by_genre <- readr::read_csv('./excel_files/data_by_genres.csv')
by_year <- readr::read_csv('./excel_files/data_by_year.csv')

main <- drop_na(main)
by_year <- drop_na(by_year)
by_genre <- drop_na(by_genre)
```

## Final Project Questions

**1.** Does a success of a song depend on the date of the song released?
```{r}
q1 <- by_year %>% 
      group_by(year) %>%
      summarize(popularity = mean(popularity)) %>% 
      arrange(desc(popularity)) %>%
      head(n = 20)
q1
```

Based on this graph it looks like a songs "success" or popularity doesnt matter when it was released as there is no patteren to why songs are popular in some years compared to other years.


**2.** Does the popularity of a song depend on the danceability and energy?
```{r}
main_danceability_ave <- mean(main$danceability)
main_danceability_ave

main_energy_ave <- mean(main$energy)
main_energy_ave
q2 <- main %>% 
      group_by(popularity) %>%
      select(popularity, artists, name, danceability, energy) %>% arrange(desc(popularity)) %>%
      head(n = 20)
q2
```

You can see that for a song to be decently popular that the song needs to have a balance between dancebility and energy. The song cant have the biggest dancebility without the same level of energy the only outlier from this is that Bille Eilish's songs are all catchy but have little to no energy so it makes sense why her numbers are the way that they are.



