---
title: "Sakeths_analysis"
author: "Saketh Jonnadula"
date: "4/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r warning=FALSE, message=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)

main <- readr::read_csv('./excel_files/data.csv')
by_artist <- readr::read_csv('./excel_files/data_by_artist.csv')
by_genre <- readr::read_csv('./excel_files/data_by_genres.csv')
by_year <- readr::read_csv('./excel_files/data_by_year.csv')

main <- drop_na(main)
by_year <- drop_na(by_year)
```

## Final Project Questions

**1.** Does a success of a song depend on the date of the song released?
```{r}
q1 <- by_year %>% 
      group_by(year) %>%
      summarize(popularity = mean(popularity)) %>% 
      arrange(desc(popularity)) %>%
      head(n = 20)
q1
```

Based on this graph it looks like a songs "success" or popularity doesnt matter when it was released as there is no patteren to why songs are popular in some years compared to other years.


**2.** Does the popularity of a song depend on the danceability and loudness?
```{r}
q2 <- main %>% 
      group_by(popularity) %>%
     select(popularity, artists, name, danceability, loudness) %>% arrange(desc(popularity)) %>%
      head(n = 20)
q2
```

I think this is what we need lmk if i need to change this



