---
title: "Tanner's Analysis"
author: "Tanner Dunn"
date: "4/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)

main <- readr::read_csv('./excel_files/data.csv')
by_artist <- readr::read_csv('./excel_files/data_by_artist.csv')
by_genre <- readr::read_csv('./excel_files/data_by_genres.csv')
by_year <- readr::read_csv('./excel_files/data_by_year.csv')

main <- drop_na(main)
```

## Final Project Questions

**1.** Does a success of a song depend on the date of the song released?
```{r}

```


**2.** Does the popularity of a song depend on the danceability and loudness?
```{r}

```


**3.** What were the five most popular songs in 2020? Is there a correlation with popularity and energy?
```{r}
#not finished
q3 <- main %>%
      filter(year == 2020) %>%
      select(artists, name, popularity, energy) %>%
      arrange(desc(popularity)) %>%
      head(5)

```


**4.** Analyze how song trends (danceability, energy, etc..), changed throughout each year.
```{r}
q4 <- main %>% 
      group_by(year) %>%
      summarise(danceability = mean(danceability),
                acousticness = mean(acousticness),
                energy = mean(energy),
                valence = mean(valence),
                liveness = mean(liveness))

q4
```

```{r}
#Plot for song trends
q4 <- q4 %>% pivot_longer(danceability:liveness, names_to = 'trend', values_to = 'value')

q4_plot <- q4 %>% 
      ggplot(aes(x = year, y = value, color = trend)) + geom_line() + 
      ggtitle("Trends Throughout the Years")

q4_plot
```


**5.** Analyze relationship between temp and acousticness.
```{r}

```


**6.** What is the greatest predictor of a song's popularity? 
```{r}
#This is more of a regression problem which was not covered in this class (Maybe Remove?)
```


**7.** Who are the most popular one hit wonders?
```{r}
one_hit_wonder <- main %>% 
   group_by(artists = artists) %>%
   summarise(Num_track = n(), Popularity = mean(popularity)) %>%
   filter(Num_track == 1) %>%
   top_n(5, wt = Popularity)

   ggplot(one_hit_wonder, aes(x = reorder(artists, -Popularity), weight = Popularity)) + geom_bar() + coord_cartesian(ylim=c(75,100)) + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + ylab("Popularity") + ggtitle("Most Popular One Hit Wonders")
```

Now that we found the popular one hit wonder artists or groups, lets look at the one song they released
```{r}
one_hit_names <- inner_join(main, one_hit_wonder, by = 'artists')
summarise(one_hit_names, name, artists)
```


**8.** How has Post Malone (My Favorite Artist) Popularity changed over the past few years
```{r}
dat <- main %>%
   group_by(year = year, artists = artists) %>%
   summarise(popularity = mean(popularity)) %>%
   filter(artists == "['Post Malone']")

ggplot(dat, aes(x = year, weight = popularity)) + geom_bar() + ylab('Popularity') + coord_cartesian(ylim=c(60, 80))
   
```

Post Malone has dropped 3 albums, the first in 2016, second in 2018, and the third in 2019, therefore those are the years he has a popularity value. It is clear that he is becoming more and more popular with each album that he releases. 


**9.**
```{r}

```

